My title

### 2024-09-25 paper/paper.qmd
Update LLM usage and add reference

library(tidyverse)
library(opendatatoronto)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

>>>>

library(tidyverse)
library(opendatatoronto)
library(here)

# Load the analysis data
data <- read_csv(here::here("data", "analysis_data", "analysis_data.csv"))
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| warning: false
#| message: false
